VCF file filtering by common garden site

### 2020-01-25 analysis/common-garden-allele-balancing/1_VCF_file_filtering_by_common_garden_site.Rmd
Plots and Writeup for Common Garden Allele Balancing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bigsnpr)
library(switchgrassGWAS)
load("~/Github/pvdiv-phenology-gxe/data/phenotypes_2019.rda")
load("~/Github/pvdiv-phenology-gxe/data/sites.rda")
```

@@

```{r}
colSums(!is.na(phenotypes_wide_2019))
i=1
for(i in 1:10){
site <- sites$Site[i]

@@

vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/PKLE_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/PKLE_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/BRKG_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/BRKG_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/CLMB_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/CLMB_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/FRMI_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/FRMI_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KBSM_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KBSM_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KING_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KING_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/LINC_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/LINC_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/OVTN_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/OVTN_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/STIL_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/STIL_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/TMPL_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/TMPL_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/PKLE_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/PKLE_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/BRKG_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/BRKG_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/CLMB_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/CLMB_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/FRMI_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/FRMI_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KBSM_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KBSM_2018j &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KING_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KING_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/LINC_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/LINC_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/OVTN_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/OVTN_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/STIL_2018 --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/STIL_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_732g_33M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/TMPL_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/TMPL_2018 &

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bigsnpr)
library(switchgrassGWAS)
load("~/Github/pvdiv-phenology-gxe/data/phenotypes_2019.rda")
load("~/Github/pvdiv-phenology-gxe/data/phenotypes_2018.rda")
load("~/Github/pvdiv-phenology-gxe/data/sites.rda")
```

@@

```{r}
colSums(!is.na(phenotypes_wide_2019))
i=7
for(i in 1:10){
site <- sites$Site[i]

@@

vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/PKLE_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/PKLE_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/BRKG_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/BRKG_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/CLMB_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/CLMB_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/FRMI_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/FRMI_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KBSM_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KBSM_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KING_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KING_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/LINC_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/LINC_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/OVTN_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/OVTN_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/STIL_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/STIL_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/TMPL_2019 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/TMPL_2019 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/PKLE_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/PKLE_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/BRKG_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/BRKG_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/CLMB_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/CLMB_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/FRMI_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/FRMI_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KBSM_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KBSM_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/KING_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/KING_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/LINC_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/LINC_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/OVTN_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/OVTN_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/TMPL_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/TMPL_2018 &
vcftools --gzvcf /home/SharedUser/PV/NatPop/33dot9MSite_Unimputed/Pvirgatum_V5_GWAS_630g_33dot9M.vcf.gz --keep /home/alice/Github/pvdiv-phenology-gxe/analysis/common-garden-allele-balancing/STIL_2018 --freq --out /home/alice/Github/pvdiv-phenology-gxe/large-files/Site-by-year-allele-frequencies/STIL_2018 &
